si: code and prose exploring Spatial Interaction models

### 2022-04-23 README.qmd
Rename constraint_p to constraint_production #12
Former-commit-id: 4529e7d21166bac415501a34da0050828d3dfdb6

```{r distance}
library(si)
library(dplyr)
# prepare OD data
od = si_to_od(
  origins = si_zones,        # origin locations
  destinations = si_zones,   # destination locations
  max_dist = 5000            # maximum distance between OD pairs
  )
# specify a function
gravity_model = function(beta, d, m, n) {
  m * n * exp(-beta * d / 1000)
} 
# perform SIM
od_res = si_calculate(
  od,
  fun = gravity_model,
  d = distance_euclidean,
  m = origin_all,
  n = destination_all,
  constraint_p = origin_all,
  beta = 0.3
  )
# visualize the results
plot(od_res$distance_euclidean, od_res$interaction)
```

What just happened?
We created an 'OD data frame' with the function `si_to_od()` from geographic origins and destinations, and then estimated a simple 'production constrained' (with the `constraint_p` argument) gravity model based on the population in origin and destination zones and a custom distance decay function with `si_calculate()`.
As the example above shows, the package allows/encourages you to define and use your own functions to estimate the amount of interaction/movement between places.

@@

```{r}
od_res = od %>% 
  si_calculate(fun = gravity_model, 
               m = origin_all,
               n = destination_all,
               d = distance_euclidean,
               constraint_p = origin_all,
               beta = 0.3)
od_res %>% 
  select(interaction)
```

>>>>

```{r distance}
library(si)
library(dplyr)
# prepare OD data
od = si_to_od(
  origins = si_zones,        # origin locations
  destinations = si_zones,   # destination locations
  max_dist = 5000            # maximum distance between OD pairs
  )
# specify a function
gravity_model = function(beta, d, m, n) {
  m * n * exp(-beta * d / 1000)
} 
# perform SIM
od_res = si_calculate(
  od,
  fun = gravity_model,
  d = distance_euclidean,
  m = origin_all,
  n = destination_all,
  constraint_production = origin_all,
  beta = 0.3
  )
# visualize the results
plot(od_res$distance_euclidean, od_res$interaction)
```

What just happened?
We created an 'OD data frame' with the function `si_to_od()` from geographic origins and destinations, and then estimated a simple 'production constrained' (with the `constraint_production` argument) gravity model based on the population in origin and destination zones and a custom distance decay function with `si_calculate()`.
As the example above shows, the package allows/encourages you to define and use your own functions to estimate the amount of interaction/movement between places.

@@

```{r}
od_res = od %>% 
  si_calculate(fun = gravity_model, 
               m = origin_all,
               n = destination_all,
               d = distance_euclidean,
               constraint_production = origin_all,
               beta = 0.3)
od_res %>% 
  select(interaction)
```
